Learning From Massive Noisy Labeled Data for Image Classification

### 2015-04-08 paper.tex
Update the abstract

%%%%%%%%% ABSTRACT
\begin{abstract}
Large-scale supervised datasets are crucial to train deep neural networks for various computer vision problems. However, obtaining a massive amount of well labeled data is usually very expensive and time consuming. In this paper, we introduce a general framework to train deep nets with only limited number of clean labels and millions of easily obtained noisy labels. We model label noises with a graphical probabilistic framework and further integrate it into the deep learning system. To demonstrate the performance of our approach, we collect a large scale clothing classification dataset with both noisy and clean labels. We demonstrate the effectiveness of our approach on this dataset, showing the possibility of learning a strong deep model with only a small amount of clean labels.
\end{abstract}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.95\linewidth]{figure/overview.pdf}
\end{center}
\caption{Overview of our approach. Labels of web images often suffer from different types of noise. A label noise model is proposed to detect and correct the wrong labels. The corrected labels are used to train the underlying CNNs.}
\label{fig:overview}
\end{figure}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Large-scale supervised datasets are crucial to train convolutional neural networks (CNNs) for various computer vision problems. However, obtaining a massive amount of well labeled data is usually very expensive and time consuming. In this paper, we introduce a general framework to train CNNs with only limited number of clean labels and millions of easily obtained noisy labels. We describe label noises with a probabilistic graphical model and further integrate it into an end-to-end deep learning system. To demonstrate the effectiveness of our approach, we collect a large-scale clothing classification dataset with both noisy and clean labels. Experiments on this dataset show that our model can better detect and correct the wrong labels, which benefits the training of underlying CNNs.
\end{abstract}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.95\linewidth]{figure/overview.pdf}
\end{center}
\caption{Overview of our approach. Labels of web images often suffer from different types of noise. A label noise model is proposed to detect and correct the wrong labels. The corrected labels are used to train underlying CNNs.}
\label{fig:overview}
\end{figure}
